%!TEX root = iso_cpp_modules_ecosystem_technical_report.tex

\rSec0[source]{Source Files}

\indextext{source files|(}%

\pnum For tooling purposes, there are two main categories of source
files: the primary source file, and included files. The primary source
file of a translation unit is the one used to start the first phase of
the translation.  The included files contribute to translation unit by
methods of ``Source file inclusion''.

\pnum With the exception of header units, the translation unit type
can be defined unambiguously by the contents of the primary source
file because of preprocessing restrictions established by the \Cpp{}
Standard. Header units require additional information at the tooling
level.

\rSec1[source.types]{Translation Unit Types}

\indexdefn{importable units}%
\definition{importable units}{source.types.importable}%
%
Translation units that must be translated before other translation
units (usually via the encoding of a binary module interface file),
such that the usage of ``import'' statements can be correctly
interpreted.

\indexdefn{module interface units}%
\definition{module interface units}{source.types.interface}%
%
Importable units that contribute to the ``external interface'' of a
named module with declaration and definitions within the purview of a
named module.

\indexdefn{primary module interface unit}%
\definition{primary module interface unit}{source.types.primary-interface}%
%
Module interface unit without a partition, it can be unambiguosly
identified by the presence of the export-keyword and the absense of a
module-partition. There can be only one primary unit for each module.

\indexdefn{module interface partition unit}%
\definition{module interface partition unit}{source.types.interface-partition}%
%
Module interface unit with a module-partiton. It can be unambiguously
identified by the presence of both export-keyword and the presence of
module-partition. There can only be one unit for a given partition
name.

\indexdefn{internal module partition unit}%
\definition{internal module partition unit}{source.types.internal-partition}%
%
Importable translation units with declarations and definitions in the
purview of a given named module, but that do not contribute to its
``external interface''. It can be unambiguously identified by the
absense of the export-keyword and the presence of module-partition. An
internal partition may or may not be reachable by the module interface
units. An internal partition that is not reachable by the interface
units is not required to be made available to translation units
outside the module.

\indexdefn{header unit}%
\definition{header unit}{source.types.header-unit}%
%
Header units are the independent translation of what would otherwise
be available via source inclusion. They are not identifiable directly
by the contents of the primary source file. Additional information is
needed at the tooling level to identify them. Implementations are not
required to accept any header or header file that could be included to
be also importable.

\indexdefn{module implementation unit}%
\definition{module implementation unit}{source.types.implementation}%
%
Module implementation units contain definitions in the module purview
that were omitted on the interface units and internal partitions
units. It can be unambiguously identified by the absense of the
export-keyword and the absence of module-partition. It may also
contain other declarations in the module purview, but those are not
reachable from the module interface or internal partitions.

\indexdefn{non-module unit}%
\definition{non-module unit}{source.types.non-module}%
%
Translation units without a module-declaration that are not header
units.

\rSec1[source.file-extensions]{Filename Extensions}

\pnum TODO: \href{https://github.com/cplusplus/modules-ecosystem-tr/issues/20}{modules-ecosystem-tr\#20}

\indextext{source files|)}%

